The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-05-14 RET_Hosts_CWR.tex

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[DES Collaboration]{
\parbox{\textwidth}{
\Large
P.~Wiseman,$^{1}$
M.~Pursiainen,$^{1}$
M.~Childress,$^{1}$
E.~Swann,$^{2}$
M.~Smith,$^{1}$
L.~Galbany,$^{3}$
C.~Lidman,$^{4}$
T.~M.~Davis,$^{5}$
A.~M\"oller,$^{6}$
B.~P.~Thomas,$^{7,2}$
C.~Frohmaier,$^{2}$
R.~J.~Foley,$^{8}$
S.~R.~Hinton,$^{5}$
L.~Kelsey,$^{1}$
G.~F.~Lewis,$^{9}$
M.~Sako,$^{10}$
D.~Scolnic,$^{11}$
M.~Sullivan,$^{1}$
M.~Vincenzi,$^{2}$
B.~E.~Tucker,$^{4}$
C.~P.~Guti\'errez,$^{1}$
T.~M.~C.~Abbott,$^{12}$
M.~Aguena,$^{13,14}$
S.~Allam,$^{15}$
J.~Annis,$^{15}$
E.~Bertin,$^{16,17}$
S.~Bhargava,$^{18}$
D.~Brooks,$^{19}$
D.~L.~Burke,$^{20,21}$
A.~Carnero~Rosell,$^{7}$
D.~Carollo,$^{7,22}$
M.~Carrasco~Kind,$^{23,24}$
J.~Carretero,$^{25}$
M.~Costanzi,$^{26,27}$
L.~N.~da Costa,$^{14,28}$
H.~T.~Diehl,$^{15}$
P.~Doel,$^{19}$
S.~Everett,$^{8}$
J.~Frieman,$^{15,29}$
J.~Garc\'ia-Bellido,$^{30}$
E.~Gaztanaga,$^{31,32}$
K.~Glazebrook,$^{33}$
D.~Gruen,$^{34,20,21}$
R.~A.~Gruendl,$^{23,24}$
J.~Gschwend,$^{14,28}$
G.~Gutierrez,$^{15}$
K.~Honscheid,$^{35,36}$
D.~J.~James,$^{37}$
K.~Kuehn,$^{38,39}$
N.~Kuropatkin,$^{15}$
M.~Lima,$^{13,14}$
M.~A.~G.~Maia,$^{14,28}$
J.~L.~Marshall,$^{40}$
P.~Martini,$^{35,41}$
F.~Menanteau,$^{23,24}$
R.~Miquel,$^{42,25}$
A.~Palmese,$^{15,29}$
F.~Paz-Chinch\'{o}n,$^{43,24}$
A.~A.~Plazas,$^{44}$
A.~K.~Romer,$^{18}$
E.~Sanchez,$^{45}$
M.~Schubnell,$^{46}$
S.~Serrano,$^{31,32}$
I.~Sevilla-Noarbe,$^{45}$
N.~E.~Sommer,$^{4}$
E.~Suchyta,$^{47}$
M.~E.~C.~Swanson,$^{24}$
G.~Tarle,$^{46}$
D.~L.~Tucker,$^{15}$
T.~N.~Varga,$^{48,49}$
and A.~R.~Walker$^{12}$
\begin{center} (DES Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{Affiliations are listed at the end of the paper}
}
% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[DES Collaboration]{
\parbox{\textwidth}{
\Large
P.~Wiseman,$^{1}$
M.~Pursiainen,$^{1}$
M.~Childress,$^{1}$
E.~Swann,$^{2}$
M.~Smith,$^{1}$
L.~Galbany,$^{3}$
C.~Lidman,$^{4}$
T.~M.~Davis,$^{5}$
C.~P.~Guti\'errez,$^{1}$
A.~M\"oller,$^{6}$
B.~P.~Thomas,$^{2}$
C.~Frohmaier,$^{2}$
R.~J.~Foley,$^{7}$
S.~R.~Hinton,$^{5}$
L.~Kelsey,$^{1}$
R.~Kessler,$^{8,9}$
G.~F.~Lewis,$^{10}$
M.~Sako,$^{11}$
D.~Scolnic,$^{12}$
M.~Sullivan,$^{1}$
M.~Vincenzi,$^{2}$
T.~M.~C.~Abbott,$^{13}$
M.~Aguena,$^{14,15}$
S.~Allam,$^{16}$
J.~Annis,$^{16}$
E.~Bertin,$^{17,18}$
S.~Bhargava,$^{19}$
D.~Brooks,$^{20}$
D.~L.~Burke,$^{21,22}$
A.~Carnero~Rosell,$^{23}$
D.~Carollo,$^{24}$
M.~Carrasco~Kind,$^{25,26}$
J.~Carretero,$^{27}$
M.~Costanzi,$^{28,29}$
L.~N.~da Costa,$^{15,30}$
H.~T.~Diehl,$^{16}$
P.~Doel,$^{20}$
S.~Everett,$^{7}$
J.~Frieman,$^{16,9}$
J.~Garc\'ia-Bellido,$^{31}$
E.~Gaztanaga,$^{32,33}$
K.~Glazebrook,$^{34}$
D.~Gruen,$^{35,21,22}$
R.~A.~Gruendl,$^{25,26}$
J.~Gschwend,$^{15,30}$
G.~Gutierrez,$^{16}$
K.~Honscheid,$^{36,37}$
D.~J.~James,$^{38}$
K.~Kuehn,$^{39,40}$
N.~Kuropatkin,$^{16}$
M.~Lima,$^{14,15}$
M.~A.~G.~Maia,$^{15,30}$
J.~L.~Marshall,$^{41}$
P.~Martini,$^{36,42}$
F.~Menanteau,$^{25,26}$
R.~Miquel,$^{43,27}$
A.~Palmese,$^{16,9}$
F.~Paz-Chinch\'{o}n,$^{44,26}$
A.~A.~Plazas,$^{45}$
A.~K.~Romer,$^{19}$
E.~Sanchez,$^{23}$
M.~Schubnell,$^{46}$
S.~Serrano,$^{32,33}$
I.~Sevilla-Noarbe,$^{23}$
N.~E.~Sommer,$^{4}$
E.~Suchyta,$^{47}$
M.~E.~C.~Swanson,$^{26}$
G.~Tarle,$^{46}$
B.~E.~Tucker,$^{4}$
D.~L.~Tucker,$^{16}$
T.~N.~Varga,$^{48,49}$
and A.~R.~Walker$^{13}$
\begin{center} (DES Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{Affiliations are listed at the end of the paper}
}
% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}
